---
title: "finalProject"
author: "x"
date: "9/29/2021"
output: html_document
---

#*Objective*

>I would like to investigate what specific reason that led to the increase in NC population, >>is it because people found a better job opportunity, affordable housing (compared with the >>other states )or because of Nc is a good place for retirement? Also, I would like to map >>cities in NC that most people are moving to and what cities and countries that they are >>moving from.


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(skimr)
library(usmap)
library(ggplot2)
library( ggforce )
library(patchwork)
```

***A. Load all Data ***

```{r message=FALSE, warning=FALSE}
homesold <-read_csv("homes_sold.csv")
popd <-read_csv("growth.csv")
gusa <- map_data("state")
migration <-read_csv("migration_from.csv")
dominants <-read_csv("dominant.csv")
costliv<- read_csv("cost_living.csv")

```


---------------------------------------------------------

***Plot #1 New house sold summary***   



```{r  message=FALSE, warning=FALSE}
homesold %>% ggplot( aes( New_h_S ) ) + 
  geom_boxplot(fill = "white", colour = "#3366FF",
               outlier.colour = "red", outlier.shape = 1)+
  labs( title="sammuraize numbers of new house sold ", 
        x="Years"
  )+
  theme(panel.background = element_rect(fill = "linen"))
```

this plot summarize New house sold data 

  Min.   : 306000  
  1st Qu.: 505000  
  Median : 757000  
  Mean   : 827516  
  3rd Qu.:1012000  
  Max.   :1815000

--------------------------------------------------------------------

***Plot #2 NC New House Sold by population  over year***   

```{r}

highlight_df <- homesold %>% filter(Year>=2016)

homesold %>% ggplot( aes(Year, New_h_S / population )) +
  geom_line()+
    geom_line(data=highlight_df,color ="red")+
  scale_x_continuous( breaks = scales::breaks_extended(n=20) )+
  labs( title="NC New House Sold by population  over years ", 
        subtitle="From 1990-2020", 
        x="Years", 
        y="New house sold by population" )+
theme(plot.title = element_text(size = 20, color = "#1b98e0"),
     plot.subtitle = element_text(size = 10, color = "red"))+
  theme(plot.background = element_rect(colour = "red", size = 2))




```

 we notice that there is a huge increase of house sold from 2016 to 2020.
 
------------------------------------------------------------------------ 

***Plot #3 % of grow by state***   

```{r}




highlight_tf <- popd %>% filter(region == "north carolina" )


popd %>% ggplot( aes( x = reorder(region, -Percent), Percent ) ) + 
  geom_bar( stat = "identity" ) +
  geom_bar(stat = "identity", data= highlight_tf, fill ="red")+
  scale_fill_discrete()+ 
  guides( x = guide_axis(angle = 90) )+
  labs( title="% of growth for each state from the highiest  to the lowest ", 
        x ="States", 
        y="Percentage of growth" )+
   annotate(geom = "text", x = 8, y = 0.04,
            label = "the 9th growing state", hjust = "left" ,color="red")+
    theme(plot.title = element_text(hjust = 0.5, color="red")) +
 theme(plot.background = element_rect(fill = "lightblue"))
  

```

North Carolina is the 9th growing State


------------------------------------------------------------------------

```{r out.width = '80%' }
#8----------------------------same Plot as #6-----------------

dominants %>% ggplot( aes( ratio_sex, log(Pop) )) +
 geom_point(data = filter(dominants, State == "North Carolina"),
            color = "red",
            size = 3) +
  geom_point(aes( color=factor(State)))+
 facet_wrap(~dominant_sex)+
geom_mark_ellipse( aes( label= dominant_group, group = dominant_group
 ) ) +
  labs( title="Dominant Sex and groupe age by states")+
  theme(plot.title = element_text(hjust = 0.5, color="blue", size = 15))+
   guides(col = FALSE)+
    theme_minimal() 



```

***Plot #4 Mapping density population *** 

```{r}
state_centroids <- summarize(group_by(gusa, region),
                             x = mean(range(long)), y = mean(range(lat)))

state_pops <- inner_join(popd, state_centroids, "region")

ggplot(gusa) +
  geom_polygon(aes(long, lat, group = group),
               fill = NA, color = "black") +
   geom_point(aes(x, y, size = Pop), data = state_pops, color="red") +
   scale_size_area() +
  coord_map("bonne", parameters=45) +
  ggthemes::theme_pander()+
   labs( title="Mapping Density Population Across USA")+
  theme(legend.position = "none")+
  theme(plot.title = element_text(hjust = 0.5, color="blue"))
```

North Carolina  is one of the densest population 

------------------------------------------------------------------------

***Plot #5 the most state sending migrant  to North carolina*** 



```{r}
#7---------------Migration-------------------------


migration_pops <- inner_join(migration, state_centroids, "region")

sp2 <- select(migration_pops, region = region, T_North_Carolina)
spr2 <- mutate(sp2, rankpop = rank(T_North_Carolina))

gusa_rpop <- left_join(gusa, spr2, "region")

ggplot(gusa_rpop) +
  geom_polygon(aes(long, lat, group = group, fill = rankpop )) +
  coord_map("bonne", parameters=45, ) +
  ggthemes::theme_map()+
  labs( title="Rank the Most sending Migrant to NC")+
  theme(plot.title = element_text(hjust = 0.5, color="blue", size = 15))
```

The dark area is the most sending migrant like North Dakota ,South Dakota, New York ,Nevada

------------------------------------------------------------------------

***Plot #6  Dominant Sex and groupe age by State*** 



```{r }

dominants %>% ggplot( aes( ratio_sex, log(Pop) )) +
 geom_point(data = filter(dominants, State == "North Carolina"),
            color = "red",
            size = 3) +
  geom_point(aes( color=factor(State)))+
 facet_wrap(~dominant_sex)+
geom_mark_ellipse( aes( label= dominant_group, group = dominant_group
 ) ) +
  labs( title="Dominant Sex and groupe age by states")+
  theme(plot.title = element_text(hjust = 0.5, color="blue", size = 15))+
    theme_minimal() +
  theme(
  legend.background = element_rect(
    fill = "lemonchiffon", 
    colour = "grey50", 
    size = 1
  )
)



```


this plot show hat Nc has a Female dominant Sex with adult dominant group age   

------------------------------------------------------------------------

***Plot #7  compare some cost of living between the top 10 growing states *** 


```{r}
#9----------------------------plot
filter_state <- costliv %>% filter(State == 'North Carolina'| 
                                    State == 'California'|
                                    State == 'Texas'|
                                    State == 'Florida'|
                                    State == 'New York'|
                                    State == 'Illinois'|
                                    State == 'Ohio'|
                                    State == 'Georjia'|
                                    State == 'Michgan'
                                   )  
highlight_GC <- filter_state %>% filter(State== "North Carolina")

GC<-filter_state %>% ggplot( aes(x = reorder(State, +groceryCost) , groceryCost )) +
    geom_point()+
geom_point(data=highlight_GC, color ="red")+
  guides( x = guide_axis(angle = 90) )


HC<-filter_state %>% ggplot( aes(x = reorder(State, +housingCost) , housingCost )) +
  geom_point() +
  geom_point(data=highlight_GC, color ="red")+
  guides( x = guide_axis(angle = 90) )

UC<-filter_state %>% ggplot( aes(x = reorder(State, +utilitiesCost) , utilitiesCost )) +
  geom_point() +
  geom_point(data=highlight_GC, color ="red")+
  guides( x = guide_axis(angle = 90) )

TC<-filter_state %>% ggplot( aes(x = reorder(State, +transportationCost) , transportationCost )) +
  geom_point() +
  geom_point(data=highlight_GC, color ="red")+
  guides( x = guide_axis(angle = 90) )+
  



```

```{r}
#GC+UC+HC+

  TC
```

North Carolina is the 3th state  cheapest in Utility Cost , 4th cheapest in Grocery Cost ,2nd cheaper in housing cost and 2nd also Transportation


***B. Conclusion *** 

According to the few Plot that I was able to make .The reason why North Carolina is growing Because of cost of leaving is less comparing to some other States 






